Malacology: A Programmable Storage System

### 2017-01-30 paper/paper.tex
paper: add implementation overview figure
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

The guiding principle
is to re-use existing services and extend them so that these services can be
\emph{programmed}. We accomplish programmability of a service by exporting
bindings (or ``hooks'') for an interpreted programming language so that
programming can occur without having to restart the storage system (see also
below,~\S\ref{sec:durability}). Table~\ref{table:examples} shows the internal services from Ceph that we expose in the Malacology prototype via Lua~\cite{ierusalimschy1996lua} bindings.

>>>>

\begin{figure}[tbp]
\centering
\includegraphics{figures/implementation-overview.png}
\caption{Malacology is implemented on the daemons and clients that run in a
Ceph cluster. The gray callout bubbles show where each interface is in the
storage stack and the Ceph modules, functions, and/or variables we modified.
\label{fig:implementation-overview}}
\end{figure}

The guiding principle is to re-use existing services and extend them so that
these services can be \emph{programmed}. We accomplish programmability of a
service by exporting bindings (or ``hooks'') for an interpreted programming
language so that programming can occur without having to restart the storage
system (see also below,~\S\ref{sec:durability}). Table~\ref{table:examples}
shows the internal services from Ceph that we expose in the Malacology
prototype via Lua~\cite{ierusalimschy1996lua} bindings and
Figure~\ref{fig:implementation-overview} shows where each interface lives in
the storage stack.
